### 2025-08-26 manuscript/manuscript.qmd
additional text to MS, keywords analysis altered, figures revised

The overall odds ratio for women as first authors was 1.41 [95% CI: 1.28–1.54], indicating that the odds of first authorship are 41% higher for females compared to the male authors. For coauthorship positions, the OR was 1.00 [0.91–1.09], suggesting no substantial gender difference. In contrast, the odds ratio for women as last authors was 0.73 [0.67–0.81], indicating that the odds of last authorship are 27% lower for women compared to men. Being a single author has odds ratio of 1.11 [0.95-1.29] for females, which suggests that while women are represented with relatively more single authored papers than men, the difference is not substantial (95% crosses 1.0). For the first and last authorship position, the odds ratios are significant at _p_ < .001 level.

>>>>

The overall odds ratio for women as first authors was 1.41 [95% CI: 1.28–1.54], indicating that the odds of first authorship are 41% higher for females compared to the male authors (Fisher's exact test _p_ < .001). For coauthorship positions, the OR was 1.00 [0.91–1.09], suggesting no substantial gender difference (_p_ = .96). In contrast, the odds ratio for women as last authors was 0.73 [0.67–0.81], indicating that the odds of last authorship are 27% lower for women compared to men and significantly different (_p_ < .001). Being a single author has odds ratio of 0.90 [0.78-1.05] for females, which suggests that while women are represented with relatively more single authored papers than men, the difference is not significant (_p_ = .21).
